Analysis of transit delays in the Toronto Transit Commission: 2024

### 2024-09-24 paper/paper.qmd
Update paper.qmd

---
title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
author: 
  - Dong Jun Yoon
thanks: "Code and data are available at: https://github.com/DJY1231/TTC-report-2024.git"
date: today
date-format: long
abstract: "This paper analyzes TTC delay data to understand patterns and causes of delays. It finds buses experience the most delays, especially on certain routes, while subways have frequent undocumented delays. Mechanical issues, operations, and diversions are most common delay causes. The analysis indicates the need to reduce bus delays through more vehicles or tactics like bus bridging on certain routes."
format: pdf
number-sections: true
bibliography: references.bib

@@

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

# References

>>>>

---
title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
author: "Dong Jun Yoon"
thanks: "Code and data are available at: https://github.com/DJY1231/TTC-report-2024.git"
date: today
date-format: long
abstract: "This paper analyzes TTC delay data to understand patterns and causes of delays. It finds buses experience the most delays, especially on certain routes, while subways have frequent undocumented delays. Mechanical issues, operations, and diversions are most common delay causes. The analysis indicates the need to reduce bus delays through more vehicles or tactics like bus bridging on certain routes."
format: pdf
number-sections: true
bibliography: references.bib

@@

# Data {#sec-data}
## Data Source
## Data Measurement

@@

@@

# References
R Core Team. 2023. R: A Language and Environment for Statistical Computing. Vienna,
Austria: R Foundation for Statistical Computing. https://www.R-project.org/.
